\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-06-20 Manuscript/manuscript.tex
added explanation of probability for venue effect graph

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the heat effect, since the venue
effect only captures a smaller part of the variation than the heat effect as
evident from their standard deviations. The venue effect for 2022 is
lower than that for any other year, but may not be as extreme as one would
think considering the history of reaction times going back to 1999.

>>>>

Figure~\ref{fig:VenueEffects} further illustrates the venue effect from 1999 to
2023 based on the full GLMM both with and without 2022.  The temporal patterns
of the two sets of effects look very similar, except that the positive effects
estimated with 2022 included have higher magnitude than those estimated without
2022, which compensates the negative effect of the 2022 with a large magnitude.
Both plots agree to some extent with the pattern of the boxplots in
Figure~\ref{fig:Boxplot}. The mismatch is due to the heat effect, since the venue
effect only captures a smaller part of the variation than the heat effect as
evident from their standard deviations. It is possible to calculate the extremity
of the 2022 heat effect as we know that the mean of the heat effects is $0$,
the standard deviation is $0.42$ as given by Table~\ref{tab:Gamma_parameters},
and the estimate of the 2022 heat effect is $-0.93$. We find the tail probability
to be $0.0128$ indicating there is a low chance of observing a venue effect as
extreme as 2022.
